Flexibility reduces social donations

### 2020-09-01 article-elsevier/article-elsevier.Rmd
formateo figuras

---
title: More flexibility reduces social donations
author:
  - name: Sebastián Cea-Echenique
    email: sebastian.cea@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
    footnote: 1
  - name: Claudia Toledo-Aguirre
    email: claudia.toledo@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
#   - name: Cat Memes
#     email: cat@example.com
#     affiliation: Another University
#     footnote: 2
#   - name: Derek Zoolander
#     email: derek@example.com
#     affiliation: Some Institute of Technology
#     footnote: 2
# address:
#   - code: Some Institute of Technology
#     address: Department, Street, City, State, Zip
#   - code: Another University
#     address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  # - code: 2
    # text: "Equal contribution"
abstract: |
  We exploit a change in tax donations' law to evaluate a change to more flexibility.

@@

load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
load("~/workspace/donationstax/iteraciones/Datos_seleccion_modelo.Rdata")
knitr::opts_chunk$set(fig.width=5, fig.height=5)

@@

The law 19.885 (Fig (\ref{fig:law 19885})) concerning social donations in Chile in his first version on 2003, establishes a tributary benefit of 50\% of the donation as credit discount and the other 50\% consider as spending to make the donation. To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF^[It is a Fund created by the Law on Donations with Social Purposes to support initiatives that civil society organizations present and that directly benefit people in poverty and / or people with disabilities. The Fund's resources come from donations from companies and individuals. Fund resources must be distributed through public tenders. Ministry of social development and family]). In this version of the law the limit of the donation was 4.5\% of the taxable liquid income and benefit was equally independent of the amount of the donation.

\tikzset{every picture/.style={line width=0.75pt}} 
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
\centering
\label{fig:law 19885}
\draw  [draw opacity=0][fill={rgb, 255:red, 194; green, 195; blue, 196 }  ,fill opacity=0.56 ] (81.23,63.8) .. controls (81.23,62.25) and (82.48,61) .. (84.03,61) -- (252.7,61) .. controls (254.25,61) and (255.5,62.25) .. (255.5,63.8) -- (255.5,72.2) .. controls (255.5,73.75) and (254.25,75) .. (252.7,75) -- (84.03,75) .. controls (82.48,75) and (81.23,73.75) .. (81.23,72.2) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (81.5,49.28) .. controls (81.5,47.8) and (82.7,46.6) .. (84.18,46.6) -- (164.82,46.6) .. controls (166.3,46.6) and (167.5,47.8) .. (167.5,49.28) -- (167.5,57.32) .. controls (167.5,58.8) and (166.3,60) .. (164.82,60) -- (84.18,60) .. controls (82.7,60) and (81.5,58.8) .. (81.5,57.32) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 242; green, 152; blue, 65 }  ,fill opacity=0.38 ] (167.5,49.28) .. controls (167.5,47.69) and (168.79,46.4) .. (170.38,46.4) -- (250.25,46.4) .. controls (251.84,46.4) and (253.13,47.69) .. (253.13,49.28) -- (253.13,57.92) .. controls (253.13,59.51) and (251.84,60.8) .. (250.25,60.8) -- (170.38,60.8) .. controls (168.79,60.8) and (167.5,59.51) .. (167.5,57.92) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.38 ] (81.23,78.8) .. controls (81.23,76.84) and (82.82,75.25) .. (84.78,75.25) -- (128.95,75.25) .. controls (130.91,75.25) and (132.5,76.84) .. (132.5,78.8) -- (132.5,89.45) .. controls (132.5,91.41) and (130.91,93) .. (128.95,93) -- (84.78,93) .. controls (82.82,93) and (81.23,91.41) .. (81.23,89.45) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (255.19,37.21) -- (255.31,84.39) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (132.49,63.5) -- (132.51,94.1) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (131.95,93) -- (162.37,93.74) ;
\draw [shift={(166.37,93.83)}, rotate = 181.39] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (81.5,61) -- (252.25,60.8) ;
\draw [shift={(255.25,60.8)}, rotate = 539.9300000000001] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

\draw (51.67,59.33) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
\draw (125,53.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
\draw (210.31,52.6) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
\draw (260.67,27.83) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
\draw (106.87,83.48) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 33\% MF}}};
\end{tikzpicture}

>>>>

---
title: Flexibility reduces social donations
author:
  - name: Sebastián Cea-Echenique
    email: sebastian.cea@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
    footnote: 1
  - name: Claudia Toledo-Aguirre
    email: claudia.toledo@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
#   - name: Cat Memes
#     email: cat@example.com
#     affiliation: Another University
#     footnote: 2
#   - name: Derek Zoolander
#     email: derek@example.com
#     affiliation: Some Institute of Technology
#     footnote: 2
# address:
#   - code: Some Institute of Technology
#     address: Department, Street, City, State, Zip
#   - code: Another University
#     address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  # - code: 2
    # text: "Equal contribution"
abstract: |
  We exploit a change in tax donations' law to evaluate a change to more flexibility.

@@

load("~/workspace/donationstax/data_local/Donaciones_total_graficos.Rdata")
load("~/workspace/donationstax/data_local/Datos_seleccion_modelo.Rdata")
knitr::opts_chunk$set(fig.width=5, fig.height=5)

@@

The law 19.885 (Fig (\ref{fig:law19885})) concerning social donations in Chile in his first version on 2003, establishes a tax benefit equivalent to 50\% of the donation amount as tax credit and the other 50\% consider as spending to make the donation. To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF^[It is a Fund created by the Law on Donations with Social Purposes to support initiatives that civil society organizations present and that directly benefit people in poverty and / or people with disabilities. The Fund's resources come from donations from companies and individuals. Fund resources must be distributed through public tenders. Ministry of social development and family]). In this version of the law the limit of the donation was 4.5\% of the taxable liquid income and benefit was equally independent of the amount of the donation.

\begin{figure}[h]
\label{fig:law19885}
\tikzset{every picture/.style={line width=0.75pt}} 
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
\centering
\label{fig:law 19885}
\draw  [draw opacity=0][fill={rgb, 255:red, 194; green, 195; blue, 196 }  ,fill opacity=0.56 ] (81.23,63.8) .. controls (81.23,62.25) and (82.48,61) .. (84.03,61) -- (252.7,61) .. controls (254.25,61) and (255.5,62.25) .. (255.5,63.8) -- (255.5,72.2) .. controls (255.5,73.75) and (254.25,75) .. (252.7,75) -- (84.03,75) .. controls (82.48,75) and (81.23,73.75) .. (81.23,72.2) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (81.5,49.28) .. controls (81.5,47.8) and (82.7,46.6) .. (84.18,46.6) -- (164.82,46.6) .. controls (166.3,46.6) and (167.5,47.8) .. (167.5,49.28) -- (167.5,57.32) .. controls (167.5,58.8) and (166.3,60) .. (164.82,60) -- (84.18,60) .. controls (82.7,60) and (81.5,58.8) .. (81.5,57.32) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 242; green, 152; blue, 65 }  ,fill opacity=0.38 ] (167.5,49.28) .. controls (167.5,47.69) and (168.79,46.4) .. (170.38,46.4) -- (250.25,46.4) .. controls (251.84,46.4) and (253.13,47.69) .. (253.13,49.28) -- (253.13,57.92) .. controls (253.13,59.51) and (251.84,60.8) .. (250.25,60.8) -- (170.38,60.8) .. controls (168.79,60.8) and (167.5,59.51) .. (167.5,57.92) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.38 ] (81.23,78.8) .. controls (81.23,76.84) and (82.82,75.25) .. (84.78,75.25) -- (128.95,75.25) .. controls (130.91,75.25) and (132.5,76.84) .. (132.5,78.8) -- (132.5,89.45) .. controls (132.5,91.41) and (130.91,93) .. (128.95,93) -- (84.78,93) .. controls (82.82,93) and (81.23,91.41) .. (81.23,89.45) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (255.19,37.21) -- (255.31,84.39) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (132.49,63.5) -- (132.51,94.1) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (131.95,93) -- (162.37,93.74) ;
\draw [shift={(166.37,93.83)}, rotate = 181.39] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (81.5,61) -- (252.25,60.8) ;
\draw [shift={(255.25,60.8)}, rotate = 539.9300000000001] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

\draw (51.67,59.33) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
\draw (125,53.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
\draw (210.31,52.6) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
\draw (260.67,27.83) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
\draw (106.87,83.48) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 33\% MF}}};
\end{tikzpicture}
\caption{19.885 law}
\end{figure}
